Parameter Estimation for the CES Model

### 2013-07-24 CES.Rnw
add convergence indicator

<<eval=TRUE>>=
require(plyr)
nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
  data <- loadData(countryAbbrev=countryAbbrev)
  data <- replaceColName(data, energyType, "iEToFit")
  if (nest == "(kl)e"){
    xNames <- c("iCapStk", "iLabor", "iEToFit")
  } else if (nest == "(le)k"){
    xNames <- c("iLabor", "iEToFit", "iCapStk")
  } else if (nest == "(ek)l"){
    xNames <- c("iEToFit", "iCapStk", "iLabor")
  } else {
    stop(paste("Unknown nesting option", nest, "in fitCES."))
  }
  model <- cesEst(data=data, 
                  yName="iGDP", 
                  xNames=xNames, 
                  tName="iYear",
                  method=method)
  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
}

>>>>

<<eval=TRUE>>=
require(plyr)
nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
  data <- loadData(countryAbbrev=countryAbbrev)
  data <- replaceColName(data, energyType, "iEToFit")
  if (nest == "(kl)e"){
    xNames <- c("iCapStk", "iLabor", "iEToFit")
  } else if (nest == "(le)k"){
    xNames <- c("iLabor", "iEToFit", "iCapStk")
  } else if (nest == "(ek)l"){
    xNames <- c("iEToFit", "iCapStk", "iLabor")
  } else {
    stop(paste("Unknown nesting option", nest, "in fitCES."))
  }
  model <- cesEst(data=data, 
                  yName="iGDP", 
                  xNames=xNames, 
                  tName="iYear",
                  method=method)
  res <- do(1) * coef( model ) 
  res <- transform( res, country=countryAbbrev, nest=nest, converge=model$convergence )

  return(res)
}
